Comments on Latent Ranking

### 2021-09-20 output_scripts/Cohort_level_analysis.Rmd
Revisions apr 21 (#12)
Detailed updates corresponding to a thorough revision of both the simulation studies and analyses

for(current_cohort in 1:10) {
  ### get perc for each one here
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  out_fights <- tibble(name = paste0("gamma[",1:12,"]"),
                       perc_out = rowSums(clean_data$N_count)/
                         sum(clean_data$N_count)) %>% 
    mutate(perc_out = round(perc_out, 2),
           cohort = paste0("Cohort_", current_cohort))
  in_fights <- tibble(name = paste0("zeta[",1:12,"]"),
                       perc_in = colSums(clean_data$N_count)/
                         sum(clean_data$N_count)) %>% 
    mutate(perc_in = round(perc_in, 2),
           cohort = paste0("Cohort_", current_cohort))
  ###
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  # plot_cols <- col_df %>%
  #   filter(method %in% c(
  #     "C-HP",
  #     "C-DCHP",
  #     "C-MMHP"
  #   )) %>%
  #   pull(cols)
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("gamma") ) %>% 
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP", cohort = paste0("Cohort_", current_cohort)) 
  out_perc <- out_perc %>% 
    bind_rows(out_fights)
  in_perc <- in_perc %>% 
    bind_rows(in_fights)
  cmmhp_gamma <- cmmhp_gamma %>% 
    bind_rows(all_data)
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("zeta") ) %>% 
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP", cohort = paste0("Cohort_", current_cohort)) 
  cmmhp_zeta <- cmmhp_zeta %>% 
    bind_rows(all_data)
}

@@

in_perc <- in_perc %>% 
  left_join(max_out, by = c("name", "cohort"))

cmmhp_gamma$name <- factor(cmmhp_gamma$name,
                           levels = as.character(1:12))
cmmhp_zeta$name <- factor(cmmhp_zeta$name,
                           levels = as.character(1:12))
# plot_cols
cmmhp_gamma$cohort <- factor(cmmhp_gamma$cohort, 
                             levels = paste0("Cohort_", 1:10))
cmmhp_zeta$cohort <- factor(cmmhp_zeta$cohort, 
                             levels = paste0("Cohort_", 1:10))

cmmhp_gamma %>% 
  ggplot(aes(name, value, fill = Model)) +
  geom_boxplot() +
  scale_fill_manual(values = "#FDE725FF") +
  facet_wrap(~cohort, scales = "free", ncol = 2) +
  geom_text(data = out_perc, aes(name, max_est + 0.25, label = perc_out),
            size = 2) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Out Degree", x = element_blank())

cmmhp_zeta %>% 
  ggplot(aes(name, value, fill = Model)) +
  geom_boxplot() +
  scale_fill_manual(values = "#FDE725FF") +
  facet_wrap(~cohort, scales = "free", ncol = 2) +
  geom_text(data = in_perc, aes(name, max_est + 0.25, label = perc_in),
            size = 2) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "In Degree", x = element_blank())

@@

```{r overall-fight-info}
cohort_summ <- tibble()

@@

>>>>

for(current_cohort in 1:10) {
  ### get perc for each one here
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  out_fights <- tibble(name = paste0("gamma[",1:12,"]"),
                       perc_out = rowSums(clean_data$N_count)/
                         sum(clean_data$N_count)) %>% 
    mutate(perc_out = round(perc_out, 2),
           cohort = paste0("Cohort_", current_cohort))
  in_fights <- tibble(name = paste0("zeta[",1:12,"]"),
                       perc_in = colSums(clean_data$N_count)/
                         sum(clean_data$N_count)) %>% 
    mutate(perc_in = round(perc_in, 2),
           cohort = paste0("Cohort_", current_cohort))
  ###
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("gamma") ) %>% 
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP", cohort = paste0("Cohort_", current_cohort)) 
  out_perc <- out_perc %>% 
    bind_rows(out_fights)
  in_perc <- in_perc %>% 
    bind_rows(in_fights)
  cmmhp_gamma <- cmmhp_gamma %>% 
    bind_rows(all_data)
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("zeta") ) %>% 
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP", cohort = paste0("Cohort_", current_cohort)) 
  cmmhp_zeta <- cmmhp_zeta %>% 
    bind_rows(all_data)
}

###

@@

in_perc <- in_perc %>% 
  left_join(max_in, by = c("name", "cohort"))

cmmhp_gamma$name <- factor(cmmhp_gamma$name,
                           levels = as.character(1:12))
cmmhp_zeta$name <- factor(cmmhp_zeta$name,
                           levels = as.character(1:12))
# plot_cols
cmmhp_gamma$cohort <- factor(cmmhp_gamma$cohort, 
                             levels = paste0("Cohort_", 1:10))
cmmhp_zeta$cohort <- factor(cmmhp_zeta$cohort, 
                             levels = paste0("Cohort_", 1:10))
in_perc$cohort <- factor(in_perc$cohort, 
                        levels = paste0("Cohort_", 1:10))
out_perc$cohort <- factor(out_perc$cohort,
                         levels = paste0("Cohort_", 1:10))

cmmhp_gamma %>% 
  ggplot(aes(name, value, fill = Model)) +
  geom_boxplot() +
  scale_fill_manual(values = "#FDE725FF") +
  geom_text(data = out_perc, aes(name, 2 * max_est + 1.5, label = perc_out),
            size = 2) +
  # scale_y_continuous(breaks = 3) +
  facet_wrap(~cohort, scales = "free", ncol = 2) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Out Degree", x = element_blank(),
       subtitle = "Labels denote % total fights instigated")

cmmhp_zeta %>% 
  ggplot(aes(name, value, fill = Model)) +
  geom_boxplot() +
  scale_fill_manual(values = "#FDE725FF") +
  # scale_y_continuous(breaks = 3) +
  geom_text(data = in_perc, aes(name, 2 * max_est + 1.5, label = perc_in),
            size = 2) +
  facet_wrap(~cohort, scales = "free", ncol = 2) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "In Degree", x = element_blank(),
       subtitle = "Labels denote % total fights received")

@@

```{r overall-fight-info, message=FALSE, warning=FALSE}
cohort_summ <- tibble()

@@

```
### Relationship between active fights and difference in Spearman correlation

```{r plot_percent_active_vs_spear_corr}
# cohort_summ

spear_corr_all <- tibble()

for(current_cohort in 1:10) {
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))

  ranks <- m1_ranks %>% 
    left_join(m2_ranks, by = "name") %>% 
    left_join(m3_ranks, by = "name")
  ## same think for spearman rank correlation
  m1_num <- m1_ranks %>% 
    rename(value = "C-HP") %>% 
    arrange(desc(value)) %>% 
    mutate(chp = 1:12) %>% 
    mutate(node = stringr::str_extract(name,
                                       pattern = "[:digit:]+")) %>%
    mutate(node = as.integer(node)) %>% 
    select(node, chp)

  spear_cor <- cor(rank_df[,2:5], method = "spearman")
  # spear_corr_list[[current_cohort]] <- spear_cor

  curr_spear <- as_tibble(spear_cor) %>% 
    mutate(first = c("chp", "cdchp", "cmmhp", "isi")) %>%
    pivot_longer(cols = chp:isi)

  spear_ind <- as_tibble(upper.tri(spear_cor)) %>% 
    pivot_longer(everything())

  curr_spear <- curr_spear %>% 
    bind_cols(spear_ind %>% 
                             rename(new_name = name, ind = value)) %>% 
    filter(ind == TRUE) %>% 
    select(first, name, value) %>% 
    rename(second = name) %>% 
    mutate(cohort = current_cohort)

  # %>% 
  # # filter(first != name) %>% 
  # # this removes ones which are actually identical
  # distinct(first, name, value, .keep_all = TRUE) %>% 
  # rename(second = name) %>% 
  # mutate(cohort = current_cohort)

  spear_corr_all <- spear_corr_all %>% 
    bind_rows(curr_spear)
}

spear_corr_all %>%
  left_join(cohort_summ, by = "cohort") %>% 
  filter(first == "chp") %>% 
  filter(second %in% c("cdchp", "cmmhp")) %>% 
  pivot_wider(id_cols = cohort, names_from = second, 
              values_from = c(value, act_perc)) %>% 
  select(cohort:act_perc_cdchp) %>% 
  rename(act_perc = act_perc_cdchp) %>% 
  mutate(corr_diff = value_cdchp - value_cmmhp) %>% 
  select(cohort, corr_diff, act_perc) %>% 
  ggplot(aes(corr_diff, act_perc)) +
  geom_point() +
  labs(y = "Percent fights Active", x = "Correlation Differernce",
       subtitle = "Correlation difference between C-HP/C-DCHP and C-HP/C-MMHP")
# then join this with cohort summ and do the plot
```

### 2021-09-20 output_scripts/Paper_Plots.Rmd
Revisions apr 21 (#12)
Detailed updates corresponding to a thorough revision of both the simulation studies and analyses

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/revision/",
  dev = "png", fig.height = 5, fig.width = 7,
  warning = FALSE, cache = FALSE
)

@@

```{r fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
sim_data_path <- here("output", "revisions", "lapl_check", "sim_lapl", "/")

@@

## change this to just list all files with a pattern
sims <- 1:50
sims <- sims[c(-37,-45,-46, -50)]

for(curr_sim in sims) {
  load(paste0(sim_data_path,
              "sim_model3_fit123_",
              curr_sim,
              ".RData"))

  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
  m1_ranks <- apply(f_m1, 2, mean)

@@

## this is just the mean from each simulation, not the posterior draws
```

@@

## social dsnl
fit_dsnl_inactive <- dsnl_poisson$sample(
  data = list(
    day = 21,
    Gt = social_state_day,
    c = 1,
    sigma = 1
  ),
  iter = 1000, chains = 4, control = list(adapt_delta = 0.99)
)
# print(fit_dsnl_inactive, pars = c("x"))
sim_dsnl_inactive <- rstan::extract(fit_dsnl_inactive)

@@

Need to update this to read in cmdstan results.

```{r process data for plot 10b, cache=TRUE}
library(PlayerRatings)
current_cohort <- 5
# current_cohort <- 1
load(paste(data_path, cohort_names[current_cohort],
  "/dsnl_poisson_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
load(paste(data_path, cohort_names[current_cohort],
  "/dsnl_state_separation_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
sub.types <- c("All", "Active", "Inactive")
# three methods
task.types <- paste0("day", 1:21)
data.tbl <- data.frame(array(NA, c(2000 * 3 * 21, 3)))
colnames(data.tbl) <- c("sub.type", "task.type", "data.value")
source("../lib/myGlicko.R")
#------------ gl score
df <- full_data[[cohort_names[current_cohort]]]
df <- df[df$Actor != "Start" & df$Actor != "End", ]
df1 <- expandrows(df)
df1 <- df1[order(df1$Timestamp), ] # ensure in date order
df1$event <- 1:nrow(df1)
glick.df <- df1[, c("event", "Actor", "Recipient", "score"),
                with = FALSE] # need event, actor, recipient, score
real.gl <- my_glicko(glick.df, history = TRUE, cval = 2)
clean_data_all <- cleanData(full_data[[cohort_names[current_cohort]]],
  cut_off = 1
)
day_end_idx <- unlist(lapply(c(1:21), function(x) {
  max(which(clean_data_all$day == x))
}))

@@

```{r fig-10b-rank-correlation}
par(mar = c(3, 5, 3, 1))
cx <- 1.75 # cex for axis label text;
# default is 1. bigger numbers make the text bigger, smaller, smaller.
x.ttl <- ""
# blank x-axis label
y.ttl <- "rank corr. (Glicko rank)"
ttl <- "(b)"
# y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5);
# y-axis limits. +2 at top to give room for legend
y.lim <- c(-1, 1.2)
x.lim <- c(0.5, (length(task.types)))
cols <- c("paleturquoise4", "lightgreen", "cornsilk")
shifts <- c(-0.25, 0, 0.25)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/revision/",
  dev = "png", fig.height = 5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

@@

```{r fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
sim_data_path <- here("output", "revisions", "aug_run", "sims", "/")

@@

## change this to just list all files with a pattern
sims <- list.files(sim_data_path, pattern = "sim_model3_fit123")

for(curr_sim in sims) {
  load(paste0(sim_data_path,
              curr_sim))

  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
  m1_ranks <- apply(f_m1, 2, median)

@@

## this is just the median from each simulation, not the posterior draws
```

@@

## social dsnl
fit_dsnl_inactive <- dsnl_poisson$sample(
  data = list(
    day = 21,
    Gt = social_state_day,
    c = 1,
    sigma = 1
  ),
  iter_warmup = 500,
  iter_sampling = 500,
  chains = 4,
  adapt_delta = 0.95
)
# print(fit_dsnl_inactive, pars = c("x"))
inactive_fit <- fit_dsnl_inactive$draws()
sim_dsnl_inactive <- posterior::as_draws_df(inactive_fit)

@@

```{r process data for plot 10b, cache=FALSE}
library(PlayerRatings)
current_cohort <- 5
# current_cohort <- 1
load(paste(data_path, cohort_names[current_cohort],
  "/dsnl_poisson_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
load(paste(data_path, cohort_names[current_cohort],
  "/dsnl_state_separation_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
sub.types <- c("All", "Active", "Inactive")
# three methods
task.types <- paste0("day", 1:21)
data.tbl <- data.frame(array(NA, c(2000 * 3 * 21, 3)))
colnames(data.tbl) <- c("sub.type", "task.type", "data.value")
source("../lib/myGlicko.R")
#------------ gl score
df <- full_data[[cohort_names[current_cohort]]]
df <- df[df$Actor != "Start" & df$Actor != "End", ]
df1 <- expandrows(df)
df1 <- df1[order(df1$Timestamp), ] # ensure in date order
df1$event <- 1:nrow(df1)
glick.df <- df1[, c("event", "Actor", "Recipient", "score"),
                with = FALSE] # need event, actor, recipient, score
real.gl <- my_glicko(glick.df, history = TRUE, cval = 2)
clean_data_all <- cleanData(full_data[[cohort_names[current_cohort]]],
  cut_off = 1
)
day_end_idx <- unlist(lapply(c(1:21), function(x) {
  max(which(clean_data_all$day == x))
}))

@@

```{r fig-10b-rank-correlation}
print(current_cohort)
par(mar = c(3, 5, 3, 1))
cx <- 1.75 # cex for axis label text;
# default is 1. bigger numbers make the text bigger, smaller, smaller.
x.ttl <- ""
# blank x-axis label
y.ttl <- "rank corr. (Glicko rank)"
ttl <- "(b)"
# y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5);
# y-axis limits. +2 at top to give room for legend
y.lim <- c(-1, 1.2)
x.lim <- c(0.5, (length(task.types)))
cols <- c("paleturquoise4", "lightgreen", "cornsilk")
shifts <- c(-0.25, 0, 0.25)

### 2021-09-20 output_scripts/aug_updates.Rmd
Revisions apr 21 (#12)
Detailed updates corresponding to a thorough revision of both the simulation studies and analyses

data_path <- "../output/"

@@

  mean_latent_rank <- apply(sim_cohort_mmhp$f,2,mean)

  out_degree <- apply(sim_cohort_mmhp$gamma,2,mean)
  in_degree <- apply(sim_cohort_mmhp$zeta,2,mean)

>>>>

data_path <- "../output/revisions/lapl_check/"

@@

  mean_latent_rank <- apply(sim_cohort_mmhp %>% 
                              select(starts_with("f")),2,mean)

  out_degree <- apply(sim_cohort_mmhp %>% 
                        select(starts_with("gamma")),2,mean)
  in_degree <- apply(sim_cohort_mmhp %>% 
                       select(starts_with("zeta")),2,mean)

```{r repeat-dchp}
for(current_cohort in 1:10) {
  #cat("Cohort ", current_cohort,"\n",sep="")
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_dchp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

  mean_latent_rank <- apply(sim_cohort_dchp %>% 
                              select(starts_with("f")),2,mean)

  out_degree <- apply(sim_cohort_dchp %>% 
                        select(starts_with("gamma")),2,mean)
  in_degree <- apply(sim_cohort_dchp %>% 
                       select(starts_with("zeta")),2,mean)

### 2021-09-20 output_scripts/revisions_may.Rmd
Revisions apr 21 (#12)
Detailed updates corresponding to a thorough revision of both the simulation studies and analyses

```{r simulate_20_nodes}
num_nodes <- 20
cut_off <- 3
obs_time <- 200

@@

```{r plot_pair}
start <- 20
end <- 10

@@

```{r residuals-immhp-sim}
pr_matrix <- readRDS(here("output", "revisions", "pr_matrix_immhp.RDS"))
rr_matrix <- readRDS(here("output", "revisions", "rr_matrix_immhp.RDS"))
# image(pr_matrix)

@@

```{r repeat-all-cohorts}

@@

```{r take-mean-ks/pr}
m1_ks <- tibble(Method = "C-HP",
       ks = as.vector(apply(KS_model1_array, c(2,3), mean)))

>>>>

```{r simulate_20_nodes, eval=FALSE, include=FALSE}
num_nodes <- 20
cut_off <- 3
obs_time <- 200

@@

```{r plot_pair, eval=FALSE, include=FALSE}
start <- 20
end <- 10

@@

```{r residuals-immhp-sim, eval=FALSE, include=FALSE}
pr_matrix <- readRDS(here("output", "revisions", "pr_matrix_immhp.RDS"))
rr_matrix <- readRDS(here("output", "revisions", "rr_matrix_immhp.RDS"))
# image(pr_matrix)

@@

```{r repeat-all-cohorts, eval=FALSE, include=FALSE}

@@

```{r take-mean-ks/pr, include=FALSE}
m1_ks <- tibble(Method = "C-HP",
       ks = as.vector(apply(KS_model1_array, c(2,3), mean)))
